Sound Automated Synthesis of Digital Controllers

### 2016-10-09 paper/paper.tex
Some fixes on Alessandro's comments

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is
equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer
function $G(s)$ driven by ZOH).  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use only the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

Since $G(z)$ is an approximation of $G(s)$ \red{we denote [AA: why `denote'? Shouldn't we prove that we go from the $G(s)$ TF to the $G(z,T)$ form above?]} the error in the
approximation for time $t \neq kT$ as $\Delta{G}_P$
%
\begin{align}
\small
\label{parametric_plant_tf}
\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z).
\end{align}
%
Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
percentage such that $\hat{G}(z)$ corresponds to the polynomial set of
possible values of $G(z, T): \forall T \in \mathbb{R}$. 
\red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}

@@

Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, 
\red{[the first line is not clear, there is in particular a function that is left undefined.]}
%
\begin{align}
\small
\label{FWL_tf}
&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \\
\label{digital_controller_tf}
\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
&= C(z) =\hat{C}(z) + \Delta{C}(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
\end{align}
\red{[please, how can you claim that the error enters as written? Can you show the derivation? Can you show a reference that has derived this form?]}
where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.  Since this value is
nondeterministic, the polynomial \red{[why polynomial?]} set of possible values of $\tilde G(z)$ is
denoted by $\mathfrak{G}(z)$.

@@

Considering that
the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
following equation can be written for the system in
Figure~\ref{fig:sampledsystem}
%
\begin{equation}
\resizebox{0.48\textwidth}{!}{
$\hat{Y}(z)=\nu_{1}(z)C(z)G(z)+\nu_{2}(z)G(z)+R(z)C(z)G(z)-\hat{Y}(z)C(z)G(z),$
}
\end{equation}

\noindent which can be rewritten as
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}(z)\left(R(z)+\nu_{1}(z)\right)+H_{2}(z)\nu_{2}(z)
\end{equation}
$$H_{1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}$$
$$H_{2}(z)=\frac{G(z)}{1+C(z)G(z)}$$

In the case of stability properties we need to verify the stability of both $H_{1}(z)$ and $H_{2}(z)$ to validate the stability of the whole system.
%These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
%there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
%Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
%$U(z)$.  This indicates that the quantization noise effect on a discrete
%plant model mainly depends on three main factors:
%%
%\begin{itemize}
%%
%\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
%%
%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
%%
%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible. This happens during the transient of the system, when high control actions are employed. However, it can be relevant during the steady state. A digital controller with integral action might be sufficient for eliminating such influence at steady state.
%%
%\end{itemize}
%
%An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
%Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
%$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
%$C(z)$ and error signal, {\it i.e.},
%%
%\begin{equation}
%U(z)=C(z)\cdot[R(z)-Y(z)],
%\end{equation} 
%
%\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
%\begin{equation}
%\label{eq:controlsignal}
%\resizebox{0.48\textwidth}{!}{
%$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
%}
%\end{equation} 
%
%Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
%model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
%%
%\begin{equation}
%\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
%\end{equation}
%
%\noindent where $R(z)$ can be considered as a step signal (for stabilization
%purpose) with height equal to $r$, which can be rewritten as
%%
%\begin{equation}
%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
%\end{equation}
%
%A more precise description of $\Delta{G_{Q}(z)}$ can be obtained
%considering FWL \red{[clarify what you mean with FWL, introduce FWL function explicitly and precisely]} effects on digital controller coefficients, as described in
%Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of
%the nominal $C(z)$:
%%
%\begin{equation}
%\label{eq:deltaG_final}
%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+FWL[C(z)]G(z)}{FWL[C(z)]} \cdot \frac{z-1}{z}.
%\end{equation}
%
%Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
%for quantization noise effects on closed-loop systems.  This model depends
%on the plant pulse transfer function ($G(z)$), which is described by
%Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the
%digital controller model.

>>>>

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is
equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer
function $G(s)$ driven by ZOH).  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use only the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}
Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$

%
\begin{align}
\small
\label{parametric_plant_tf}
\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z).
\end{align}
%
Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
value such that $\hat{G}(z)$ corresponds to the set of
possible polynomial forms of $G(z, T)$ that overapproximate $G(s)$.
This calculation is performed outside of the scope of this work since it depends on the nature of the tool used to obtain the $\mathcal{Z}$ form. The error comes from the bounded horizon and mathematical precision used to calculate the $\mathcal{Z}$ transform, which will be tool and user dependent.
\red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}
\green{[You are correct. It was absolutely wrong. Hopefully this explanation is clear. We use MATLAB, but still don't know the details of their implementation, so I don't have hard data on how this error is calculated.}

@@

Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
\begin{align}
\small
\label{FWL_tf}
&f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle \triangleq \tilde x = x-(x\mod\tilde x)
\end{align}
we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
\begin{align}
\label{digital_controller_tf}
\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
&= C(z) =\hat{C}(z) + \Delta{C}(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
\end{align}
where $\Delta_q\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
\red{[please, how can you claim that the error enters as written? Can you show the derivation? Can you show a reference that has derived this form?]}
\green{[the definition of f (now included) should explain it clearly]}
and $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.  Since this value is
nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
denoted by $\mathfrak{G}(z)$.

@@

Considering that
the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
following equation can be written for the system in
Figure~\ref{fig:sampledsystem}
%
\begin{equation}
\resizebox{0.48\textwidth}{!}{
$\tilde{Y}(z)=\tilde R(z)C(z)G(z)-\tilde{Y}(z)C(z)G(z)+\nu_{1}(z)+\nu_{2}(z)G(z),$
}
\end{equation}

\noindent which can be rewritten as
%
\begin{equation}
\label{eq:outputfunctions}
\tilde{Y}(z)=C(z)G(z)H(z)R(z)+H(z)\nu_{1}(z)+G(z)H(z)\nu_{2}(z)
\end{equation}
$$H(z)=\frac{1}{1+C(z)G(z)}$$

Note that $H(z)$ cancels the poles of both $G(z)$ and $C(z)$, thus we need only verify the stability of $H(z)$
to validate the stability of the whole system.
%These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
%there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
%Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
%$U(z)$.  This indicates that the quantization noise effect on a discrete
%plant model mainly depends on three main factors:
%%
%\begin{itemize}
%%
%\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
%%
%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
%%
%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible. This happens during the transient of the system, when high control actions are employed. However, it can be relevant during the steady state. A digital controller with integral action might be sufficient for eliminating such influence at steady state.
%%
%\end{itemize}
%
%An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
%Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
%$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
%$C(z)$ and error signal, {\it i.e.},
%%
%\begin{equation}
%U(z)=C(z)\cdot[R(z)-Y(z)],
%\end{equation} 
%
%\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
%\begin{equation}
%\label{eq:controlsignal}
%\resizebox{0.48\textwidth}{!}{
%$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
%}
%\end{equation} 
%
%Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
%model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
%%
%\begin{equation}
%\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
%\end{equation}
%
%\noindent where $R(z)$ can be considered as a step signal (for stabilization
%purpose) with height equal to $r$, which can be rewritten as
%%
%\begin{equation}
%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
%\end{equation}
%
%A more precise description of $\Delta{G_{Q}(z)}$ can be obtained
%considering FWL \red{[clarify what you mean with FWL, introduce FWL function explicitly and precisely]} effects on digital controller coefficients, as described in
%Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of
%the nominal $C(z)$:
%%
%\begin{equation}
%\label{eq:deltaG_final}
%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+FWL[C(z)]G(z)}{FWL[C(z)]} \cdot \frac{z-1}{z}.
%\end{equation}
%
%Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
%for quantization noise effects on closed-loop systems.  This model depends
%on the plant pulse transfer function ($G(z)$), which is described by
%Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the
%digital controller model.
